\chapter[Brief Description]{Brief Description}

\section{Architecture of Al Ice}
The architecture consists of the \emph{General}\index{General} that is the mastermind in Al Ice. He
forms plans; practically the same as creating various tasks\footnote{A task always wants to fulfill
its goal---whether it is to move to a certain location with a unit or attack with a group of units.}
that are supposed to lead it into a victorious defeat of the opponent. To do this it fetches
information that has been collected about the enemy during game play to later decide, create, and run tasks with highest
priority. Al Ice will always try to construct units that counter the opponents weapon and armor
types.

Except the general and tasks there is
\begin{inparaenum}[\itshape a\upshape)]
\item an agent for handling the enemy information that is updated when a unit enters line-of-sight.
The agent also updates the enemy information about each second, such as the current position of the
unit; 
\item a task unit handler which handles all our task units---a task unit can simply be described as
a wrapper between a unit from the spring engine and a set of tasks bound to the unit;
\item extraction point mapping where information about the extraction points are held---if a point
belongs to us, the enemy or is free; and
\item the task handler that takes care of all the active and halted tasks. It also binds and unbinds
the connection with task units and splits the load over several frames making it more CPU friendly.
\end{inparaenum}

\section{The Engine and Mod That Al Ice Runs On}
Al Ice is implemented for the Spring
engine \cite{Spring} with the modification \emph{Evolution RTS}\index{Evolution RTS}
\cite{EvolutionRTS}. Spring is only an engine and does not come with a game; therefore a separate 'game', also called mod, needs to be
downloaded. There are several games available and one of these is Evolution RTS that Al Ice is
especially built for. An important side note is that Al Ice does not cheat in any sense, no extra
resource, disabled fog of war\footnote{Fog of war being a 'fog' that lies over the battle making
it impossible to see enemy units beyond our units' sight distance; thus disabled fog of war makes
a player or AI able to see everything that happens on the map}, or any other kind of unfair
advantages.
