\chapter{Discussion}
Al Ice did splendid against the RAI v0.601, 97\% chance of winning is not bad.
On the map that Al Ice lost RAI quickly built outwards towards Al Ice and
cornered it. Since Al Ice only has a simple strategic implemented it wouldn't
just move past the first 'block', there actually was a free path to a whole
other area, and continue to expand but was instead trapped. A simple terrain
analysis would've helped it overcome this situation.

Since RAI really plays randomly there were one time when a game ended just after
about eight and a half minutes on the big map. RAI simply didn't expand at all
thus it was just for Al Ice to storm the base---which didn't have any units
because of the low metal income when it didn't expand.

Another one unofficial test was run on an extremely small map---Al Ice lost. It
probably lost due to the fact that it's main strategy is to attack with mobile
units and not to attack with defensive buildings, whereas RAI built towers that
could attack a long distance (the whole map) which destroyed our resources making
us an even easier target.

Another important fact to mention is that the RAI AI is using a map cheat, which
Al Ice isn't; this means that RAI got an unfair advantage, but this only shows the
effectiveness of the adaptive priority calculation. RAI could also have a simple
terrain analysis that can be read from the change-log\cite{RAI10}. How advanced
it is isn't mentioned.

When playing as a human against Al Ice
it's also fairly easy to win if you know how it acts. One strategy that works is to get a great deal
of extraction points on the map and build towers around those that are closest to Al Ice---its
highest attack goal is the closest extraction point. Thus it will leave the other extraction points
in peace and you can then start building up a good tower defense. You can then either continue
expanding the base through building towers and using an tower attack strategy or creating units and
attacking with them.

The second strategy is to defend a smaller area while building nukes, since Al Ice has no defense
against those at all. When you have 2-3 nukes you can start building a smaller attack group and
attack while launching the 3-4 nukes you will have by that time.

When the Shard AI gets operational one could have it battle Al Ice
and see how well the system does against the official AI of Evolution RTS. The
Shard AI uses a map cheat, so it already has an advantage---but it will nevertheless be fun to test
how it competes against it, even though Al Ice isn't advanced at all.