\Declaration{

Matteus Magnusson and Tobias Hall declare that this thesis titled, ``Adaptive
Goal Oriented Action Planning for RTS Games'' and the work presented in it are
our own. We confirm that:
\begin{itemize}
  \item This work was done wholly or mainly while in candidature for a research
  degree at this College.
  \item Where any part of this thesis has previously been submitted for a degree
  or any other qualification at this College or any other institution, this has
  been clearly stated.
  \item Where we have consulted the published work of others, this is always
  clearly attributed.
  \item Where we quoted from the work of others, the source is always given.
  With the exception of such quotations, this thesis is entirely our own work. 
  \item We have acknowledged all main sources of help.
  \item Where the thesis is based on work done by ourselves jointly with others,
  we have made clear exactly what was done by others and what we have
  contributed ourselves.  
\end{itemize} 

% Signed:\\
% \rule[1em]{25em}{0.5pt}  % This prints a line for the signature
% 
% Signed:\\
% \rule[1em]{25em}{0.5pt}  % This prints a line for the signature
% 
% Date:\\
% \rule[1em]{25em}{0.5pt}  % This prints a line to write the date
}
\clearpage

%%---------------- QUOTE ----------------

\pagestyle{empty}
\null\vfill
\textit{``You must construct additional pylons.''}

\begin{flushright}
---StarCraft\textregistered\footnote{StarCraft is a registered trademark of Blizzard Entertainment, Inc, in
the U.S. and other countries.}
\end{flushright} 
\vfill\vfill\vfill\vfill\vfill\vfill\null
\clearpage

%% ------------------ ABSTACT ----------------
\addtotoc{Abstract}
\abstract{
This thesis describes the architecture of an adaptive goal-oriented AI system that can be used for
Real-Time Strategy games. The system is at the end tested against a single opponent to test
the ability of the AI.

The system consists of a task handler agent that manages all the active and halted tasks. A
task is either low-level; used for ordering units, or high-level that can form advanced
strategies. The General forms plans that are most beneficial at the moment. For creating effective
units against the opponent a priority system is used; where the unit priorities are calculated dynamically.
}
\clearpage

%%------------------ ACKNOWLEDGEMENTS -----------------

\setstretch{1.3} 

\acknowledgements{
We would like to thank the creators of the Spring engine which has done a good job implementing an
engine that supports the modification community. The creators of Evolution RTS who has done a so
far great job with the mod, and are always quick to answer our questions.

A special thanks to our
primary supervisor during the development of this thesis: Johan Hagelb\"{a}ck who always helped us
with short notice and was a great support with his knowledge in RTS games. Our secondary
supervisor and examiner Stefan Johansson that helped us with the more specific thesis layout.

To Steve Rabin who is the editor of the AI Game Programming Wisdom-series and the authors who
contributed with their articles to him; these were very useful when designing the system. To all
those who read this thesis and contributed with finding errors in the text and sending feedback to
us.

Finally, we want to thank our families that has supported us in bad and good times.
}
\clearpage