\chapter[Result]{Result} 
The support for Evolution RTS is rather low and there were some bugs with the
Shard\footnote{Another thesis bot currently developed.} AI; thus we could not
test Al Ice against it. However Al Ice was tested against RAI v0.601, which is a bot that supports
multiple mods. The 'only' available documentation on RAI is the actual source code\cite{RAI10} with
almost no comments. This makes it hard to describe and understand why RAI uses different strategies
from time to time.

The test was performed on three different maps;
\begin{inparaenum}[1)]
\item CaisRevenge is a smaller, but not symmetric map;
\item DeltaSiegeDry which is medium sized symmetric map and is a very popular map on-line; and
\item DeltaSiegeDryRevX\_v3 is actually the DeltaSiegeDry map but mirror at the bottom making
doubling the size of the map.
\end{inparaenum}
To get a fairly good and equal result the test was run 10 times on each map where the AIs changed
start position after 5 times. The fastest, longest, and medium time is calculated, where these
values only applies when Al Ice won. The time format is minutes:seconds.

\section{Bot Tests}
\subsection{RAI} 
The test results between Al Ice and RAI v0.601.
\begin{table}[htb]
\caption{Al Ice vs. RAI}
\label{tab:alice_vs_rai}
\begin{center}
\begin{tabular}{r|c|c|c|c|c|c}
\hline
& Al Ice & RAI & \% & Medium & Fastest & Longest \\ \hline
CaisRevenge & 10 & 0 & 100\% & 16:16 & 09:10 & 25:00 \\ \hline
DeltaSiegeDry & 10 & 0 & 100\% & 20:27 & 08:57 & 31:55 \\ \hline 
DeltaSiegeDryX\_v3 & 9 & 1 & 90\% & 23:13 & 08:32 & 38:21 \\ \hline 
\end{tabular}
\end{center}
\end{table}
As can be seen in table \ref{tab:alice_vs_rai} alice won all times except
one match on the big map 'DeltaSiegeDryRevX\_v3' where Al Ice lost after half an
hour. This sums up to approximately 97\% chance that Al Ice will win over RAI.

